\documentclass[11pt]{article}
\input{common-preamble}
\usepackage{latexsym,hyperref,sddstoolkit}
\usepackage[dvips]{graphicx}

\begin{document}

\title{User's Guide for SDDS-compliant EPICS Toolkit Version 5}
\author{L. Emery, M. Borland, H. Shang, R. Soliday\\Advanced Photon Source\\ \date{\today}}
\maketitle

The SDDS-compliant EPICS toolkit is a set of software applications for
the collection or writing of data in Experimental Physics and
Industrial Control System (EPICS) database records.  Though most of
the applications essentially do rather simple operations, the
combination of these and others from the SDDS postprocessing toolkit
allows arbitrarily complicated analysis of data and control of the
accelerators at the Advanced Photon Source. These tools are general
and can be applied to devices other than accelerators under control of
EPICS.

The EPICS tools presented here read and store data to SDDS-protocol
files.  SDDS (Self-Describing Data Set)\cite{SDDS_AP1.4} refers to a
particular implementation of a self-describing file protocol used at
APS. Self-describing means that the data is referred to and accessed by
name. Thus, a user doesn't need to know, say, in which column a piece
of tabular data is located. An ASCII header contains information about the
file's data structure, i.e. definitions of structure elements
such as columns (tabular data) and parameters (single values). 

Initially adopted for complex physics simulation programs, it was clear
that the SDDS file protocol would excel in data-collecting software as
well. Typically, an EPICS tool would write EPICS data to an SDDS file with 
each readback written to a column of name corresponding to the 
EPICS database record name. Single value data that describe the experimental conditions
might be written to the file as parameters.
Once collected, the EPICS data can be further analyzed and plotted
with any of the SDDS tools described in \cite{SDDS_AP1.4}.
One can regard the EPICS tools as the layer between the EPICS
control system and more functional analyzing tools and scripts, with
SDDS protocol files as an intermediary.

Following conventional usage, EPICS database records will be referred
to as ``process variables'' or PVs in this manual.

\section{Manual Pages Overview}
\subsection{EPICS Toolkit Programs by Category}
\subsubsection{Configuration Save and Restore}
\begin{itemize}
\item \progref{sddscasr} --- a new configuration save and restore program with many unique features.
\item \progref{sddscaramp} --- Performs ramping of process variables between
the present state and the states in one or more SDDS files.
\item \progref{toggle} --- Alternates between two sets of process variable values stored in snapshot files
        at a regular interval.
        Example application: Alternate between two configurations of an accelerator for debugging
        accelerator performance.
\end{itemize}

\subsubsection{Data Collecting}
\begin{itemize}
\item \progref{sddssnapshot} --- Reads values of process variables and writes them to a snapshot file. 
        Example application: Taking successive sets of data.
\item \progref{sddsmonitor} --- Reads values of process variables and writes them to a file at regular intervals.
        Example application: archiving of system performance, investigation of glitches.
\item \progref{sddsglitchlogger} --- Reads values of process variables and writes them to a file or multifile at regular intervals when certain trigger occurs. 
        Example application: archiving of system performance, inverstigation of 
        transition-based, glitch-based and alarmed-based triggers. 
\item \progref{sddsvmonitor} --- Reads values of process variables
        and writes them to a file at regular intervals. The list of readback process
        variables is constructed by multiplying a rootname list and a suffix list.
        Example application: archiving of system performance, investigation of
        glitches.
\item \progref{sddswmonitor} --- Reads values of waveform and scalar process variables and writes them to a file at regular intervals.
        Example application: archiving of system performance, investigation of glitches.
\item \progref{sddsstatmon} --- Reads values of process variables, calculates statistics and writes them to a file at regular intervals.
        Example application: archiving of system performance.
\item \progref{sddssynchlog} --- Reads values of process variables
        synchronously.  Example application: Analyze for correlations
        between various systems.
\item \progref{sddsexperiment} --- Varies process variables and measures process variables, 
        with optional statistical analysis.
        Example application:  investigation of unforeseen physical dependences,
        measure corrector-bpm response matrices.
\item \progref{sddsvexperiment} --- Varies process variables and measures process variables, 
        with optional statistical analysis. The list of readback process variables is
        constructed by multiplying a rootname list and a suffix list.  Example
        application: investigation of unforeseen physical dependences, measure
        corrector-bpm response matrices.
\item \progref{sddsalarmlog} --- Collects alarm status of a list of process variables.
        Example applications: Logging alarms for a particular accelerator system over a period of
        many runs in order to compile a history of faults statistics.
\item \progref{sddslogger} --- Reads values of process variables and writes them to a file at regular intervals. Similar to sddsmonitor but it generates less network traffic.
\item \progref{sddslogonchange} --- Records only the values of process variables that change. This reduces the output file size if process variables do not change often.
\end{itemize}

\subsubsection{Control}
\begin{itemize}
\item \progref{sddscontrollaw} --- Reads a matrix for a control law-type equation and regulates the
values of a list of readback process variables by applying corrections to another list of process variables.
        Example application: removing slow drifts in accelerators (such as the energy of a linac beam), trajectory
        and orbit correction.
\item \progref{squishPVs} --- Minimizes the absolute values of a set of readback process variables
        by varying setpoint process variables which have a physical influence on the readback process variables.
        Example application: Reducing the size of the trajectory in a beamline without knowledge of the
        response matrix between bpms and correctors.
\item \progref{sddsoptimize} ---Minimizes or maximizes the RMS of a set of readback process variables by automatically varying setpoint process variables (or knobs composed of setpoint PVs), which have a physical influence on the readback process variables, through simplex or 1dscan method.
\item \progref{sddspvtest} ---tests the process variable given by the inputfile are out-of-range or not and sets the number of out-of-range process variables to a control PV.
\end{itemize}

\subsection{Toolkit Program Usage Conventions}
(This text in this section is borrowed from \cite{SDDS_AP1.4}.)

In order to make the multitude of Toolkit programs easier to use, the
developers have attempted to use consistent commandline argument
styles.  The Toolkit programs all require at least one commandline
argument.  Therefore, if a program is executed without commandline
arguments, it is assumed that the user is asking for help.  In this
case, a help message is printed that shows syntax and (usually)
describes the meaning of the switches.  In general, program usage is
of the following form:\\
\hspace*{5mm}{\tt programName} {\em fileNames} {\em switches}.\\
Probably the simplest example would be \\ 
\hspace*{5mm}{\tt sddsquery } {\em fileName},\\
which would invoke {\tt sddsquery} to describe the contents of an SDDS file.
A slightly more complicated example would be\\
\hspace*{5mm}{\tt sddsquery } {\em fileName} {\tt -columnList},\\
which invokes {\tt sddsquery} to list just names of columns in a file.

Programs assume that any commandline argument beginning with a minus sign ('-') is an option; all others are
assumed to be filenames.  Note that case is ignored in commandline switches.  The specific meaning of a
filename is dictated by its order on the commandline.  For example, if two filenames are given, the first
would commonly be an input file while the second would commonly be an output file.  

In some cases, a command with a single filename implies replacement of the existing file.  For example,\\
\hspace*{5mm}{\tt sddsconvert} {\em fileName} {\tt -binary}\\
would replace the named file with a binary version of the same data.   This command is completely equivalent to\\
\hspace*{5mm}{\tt sddsconvert} {\tt -binary} {\em fileName} \\
That is, unlike many UNIX commands, the position of filenames relative to options is irrelevant.

One might also wish to make a new file, rather than replacing the existing file.  This could be done by\\
\hspace*{5mm}{\tt sddsconvert} {\tt -binary} {\em fileName} {\em fileName2} \\
Note that while the option may appear anywhere on the commandline, the order of the filenames is crucial to
telling the program what to do.

In following manual pages and in the program-generated help text, program usage is described using the following
conventions:
\begin{itemize}
\item The first token on the commandline  is the name of the program.
\item Items in square-brackets ({\tt []}) are optional.  Items not in square brackets are required.
\item Items in curly-brackets ({\tt \{\}}) represent a list of choices.  The choices are separated by
a \verb+|+ character, as in\\
{\tt \{ {\em choice1} | {\em choice2} | {\em choice3} \}}
\item Items in italics are descriptions of arguments or data that must be supplied by the user.  These items are not typed 
literally as shown.
\item Items in normal print are typed as shown, with optional abbreviation.  These are
usually switch keywords or qualifiers.  Any unique abbreviation is acceptable.
\end{itemize}

In addition to using files, most toolkit programs also take input from pipes, which obviates the need for temporary
files in many cases.  For those programs that support pipes, one can employ the {\tt -pipe} option.  This option
provides a good example of what options look like.  For example, one could do the following to test binary-ascii
conversion:\\
\hspace*{5mm}{\tt sddsconvert -binary -pipe=out {\em fileName} \verb+|+ sddsconvert -ascii -pipe=in {\em fileName1} }\\
The {\tt -pipe=out} option to {\tt sddsconvert} tells it to deliver its output to a pipe; it still
expects a filename for input.  Similarly, the {\tt -pipe=in} option to {\tt sddsquery} tells it to
accept input from a pipe.  

The {\tt -pipe} switch may be given in one of five forms: {\tt -pipe}, {\tt -pipe=input,output}, {\tt
-pipe=output,input}, {\tt -pipe=input}, {\tt -pipe=output} .  The first three forms are equivalent.  In a usage
message, these forms would be summarized as {\tt -pipe[=input][,output]}.  One could also use abbreviations like
{\tt -pipe=i}, {\tt -pipe=i,o}, etc.  For convenience in the manual, the data stream from or to a pipe will 
often be referred to by the name of the file for which it substitutes.  Note that you may not deliver more
than one file on the same pipe.

\section{Manual Pages}
\label{ManualPages}
\input{cavget.tex}
\input{cavput.tex}
\input{cawait.tex}
\input{degauss.tex}
\input{sdds2dfeedforward.tex}
\input{sddsalarmlog.tex}
\input{sddsbcontrol.tex}
\input{sddscainfo.tex}
\input{sddscaplayback.tex}
\input{sddscaramp.tex}
\input{sddscasr.tex}
\input{sddscontrollaw.tex}
\input{sddsexperiment.tex}
\input{sddsfeedforward.tex}
\input{sddsgencontrolbits.tex}
\input{sddsglitchlogger.tex}
\input{sddsimagemonitor.tex}
\input{sddslogger.tex}
\input{sddslogonchange.tex}
\input{sddsmonitor.tex}
\input{sddsoptimize.tex}
\input{sddspermissive.tex}
\input{sddspvacontrollaw.tex}
\input{sddspvaglitchlogger.tex}
\input{sddspvalogger.tex}
\input{sddspvasaverestore.tex}
\input{sddspvtest.tex}
\input{sddssnapshot.tex}
\input{sddsstatmon.tex}
\input{sddssynchlog.tex}
\input{sddsvexperiment.tex}
\input{sddsvmonitor.tex}
\input{sddswget.tex}
\input{sddswmonitor.tex}
\input{sddswput.tex}
\input{squishPVs.tex}
\input{standardize.tex}
\input{toggle.tex}
\begin{thebibliography}{2}

\bibitem{SDDS_AP1.4}
    M. Borland, ``Application Programmer's Guide for SDDS Version 1.4'', APS LS Note.
    Available \href{http://ops.aps.anl.gov/manuals/SDDStoolkit/SDDStoolkit.html}{here.}

\bibitem{SDDSEPICS_PAC95}
        L. Emery, ``Commissioning Software Tools at the Advanced Photon Source'', 
        to appear in {\em Proceedings of the 1995 Particle Accelerator Conference}, May 1995, Dallas.

\bibitem{Norum2007}
        E.~Norum, ``Monopulse Beam Position Monitor Field Programmable Gate Array Function  Description'', unpublished. Available \href{https://icmsdocs.aps.anl.gov/new_docs/idcplg?IdcService=DISPLAY_URL&dDocName=APS_1198423}{here.}
\end{thebibliography}
\tableofcontents
\end{document}
