%
% Template for making SDDS Toolkit manual entries.
%
\begin{latexonly}
\newpage
\end{latexonly}

% Substitute the program name for sddspermissive
\subsection{sddspermissive}
\label{sddspermissive}

\begin{itemize}
\item {\bf description:}
\verb+sddspermissive+ monitors process variables and compares each value with
permissive ranges read from an SDDS file.  If a PV leaves its allowed range,
this program sets the message field and minor alarm of a run control PV.

\item {\bf examples:}
The following command checks the PVs listed in \verb+permissive.sdds+ for one
minute and updates the run control record \verb+myApp:Permissive+.
\begin{flushleft}{\tt
sddspermissive permissive.sdds -executionTime=60\\
  -runControlPV=string=myApp:Permissive,pingTimeout=5,pingInterval=10\\
  -runControlDescription=string=\"vacuum permissive\" -verbose
}\end{flushleft}

\item {\bf synopsis:}
\begin{flushleft}{\tt
sddspermissive <inputfile>\\
 -executionTime=<seconds>\\
 -runControlPV=string=<string>,pingTimeout=<value>,pingInterval=<value>\\
 -runControlDescription=string=<string>\\
[-verbose] [-pendIOTime=<seconds>]
}\end{flushleft}

\item {\bf files:}
\begin{itemize}
\item {\bf input file:}\par
An SDDS file with required columns \verb+ControlName+, \verb+Description+,
\verb+MinimumValue+, and \verb+MaximumValue+.  An optional \verb+Provider+
column selects the protocol.  Each page may also define parameters
\verb+MaskControlName+, \verb+MaskMinimumValue+, \verb+MaskMaximumValue+,
and \verb+MaskProvider+; when the mask PV lies within the mask range the page
is ignored.
\end{itemize}

\item {\bf switches:}
\begin{itemize}
\item {\tt -executionTime=<seconds>} --- total time to run before exiting.
\item {\tt -runControlPV=string=<pv>,pingTimeout=<value>,pingInterval=<value>} --- run
control record to set when limits are violated.
\item {\tt -runControlDescription=string=<text>} --- description placed in the run
control record.
\item {\tt -verbose} --- enable progress messages.
\item {\tt -pendIOTime=<seconds>} --- maximum time to wait for Channel Access operations.
\end{itemize}

\item {\bf see also:}
\begin{itemize}
\item \progref{sddscontrollaw}
\item \progref{sddspvtest}
\end{itemize}

\item {\bf author: R. Soliday, ANL}
\end{itemize}
