%
% sddspcas documentation.
%
\begin{sddsprog}{sddspcas}
\item \textbf{description:}
\verb+sddspcas+ is a Portable Channel Access Server (PCAS) that creates and serves EPICS process variables (PVs)
from one or more SDDS input files. Each input file must contain a \verb+ControlName+ column with PV base names.
Optional columns (e.g., \verb+Hopr+, \verb+Lopr+, \verb+ReadbackUnits+, \verb+ElementCount+, \verb+Type+) control
limits, engineering units, waveform length, and data type.

If an \verb+Equation+ column is present, PV values can be automatically updated based on expressions involving
other PVs.

On Unix-like systems, if a second \verb+sddspcas+ instance is launched under the same user account while a first instance
is already running on the same host, the second instance will forward its PV definitions to the running instance and
exit immediately. The running instance will create any PVs it is not already hosting and (unless started with
\verb+-standalone+) will append the new PVs to the configured \verb+-pcasPVFile+.

\item \textbf{examples:}
\begin{verbatim}
# Serve PVs described by an SDDS file
sddspcas pvlist.sdds

# Add a prefix to all served PVs and run for 10 minutes
sddspcas pvlist.sdds -pvPrefix=TEST: -executionTime=600

# Enable periodic noise updates
sddspcas pvlist.sdds -pvPrefix=TEST: -noise=1

# Run without checking master PV lists
sddspcas pvlist.sdds -standalone
\end{verbatim}

\item \textbf{synopsis:}
\begin{verbatim}
usage: sddspcas <inputfiles>
      [-masterPVFile=<filename>]
      [-pcasPVFile=<filename>]
      [-debugLevel=<debug level>]
      [-executionTime=<seconds>] (default=12 hours, 0=forever)
      [-pvPrefix=<PV name prefix>]
      [-noise=<rateSeconds>]
      [-runControlPV=string=<string>,pingTimeout=<value>]
      [-runControlDescription=string=<string>]
      [-standalone]
\end{verbatim}

\item \textbf{switches:}
\begin{itemize}
  \item {\tt -masterPVFile} --- SDDS file containing IOC PV names. Used to ensure no duplicate PVs are created.
  \item {\tt -pcasPVFile} --- SDDS file tracking PVs created by \verb+sddspcas+. Used to prevent multiple servers
        from advertising the same PVs and to record the serving host.
  \item {\tt -standalone} --- Do not use the master PV files unless explicitly provided.
  \item {\tt -executionTime} --- How long to run in seconds. Values less than 0.5 are treated as ``forever''.
  \item {\tt -pvPrefix} --- Prefix prepended to all PV names.
  \item {\tt -noise} --- Periodically adds small random noise to numeric PV values.
  \item {\tt -debugLevel} --- Increase diagnostic output.
  \item {\tt -runControlPV} / {\tt -runControlDescription} --- Optional run-control integration (if built with runcontrol).
\end{itemize}

\item \textbf{see also:}
\begin{itemize}
  \item \progref{sddsSoftIOC}
  \item \progref{cavget}
  \item \progref{cavput}
\end{itemize}

\item \textbf{author:} Robert Soliday, ANL/APS.
\end{sddsprog}
