%
% sddsSoftIOC documentation.
%
\begin{sddsprog}{sddsSoftIOC}
\item \textbf{description:}
\verb+sddsSoftIOC+ creates a temporary EPICS soft IOC (EPICS Base) that serves the same PV names and types as
\progref{sddspcas}, based on the same SDDS input file format.

At runtime, \verb+sddsSoftIOC+ generates an EPICS database (\verb+.db+) file in a temporary directory, starts
\verb+softIoc+ with that database, and removes the generated files on exit.

This is useful when you want ``IOC-like'' behavior using an EPICS Base \verb+softIoc+ without installing or
maintaining a static IOC application directory.

\item \textbf{examples:}
\begin{verbatim}
# Serve PVs described by an SDDS file using EPICS Base softIoc
sddsSoftIOC pvlist.sdds

# Add a prefix and run for 5 minutes
sddsSoftIOC pvlist.sdds -pvPrefix=TEST: -executionTime=300

# Use a specific EPICS Base installation
sddsSoftIOC pvlist.sdds -epicsBase=/path/to/epics-base

# Enable periodic noise updates
sddsSoftIOC pvlist.sdds -noise=1

# Run without checking master PV lists
sddsSoftIOC pvlist.sdds -standalone
\end{verbatim}

\item \textbf{synopsis:}
\begin{verbatim}
usage: sddsSoftIOC <inputfiles>
      [-masterPVFile=<filename>]
      [-pcasPVFile=<filename>]
      [-standalone]
      [-debugLevel=<debug level>]
      [-executionTime=<seconds>] (default=12 hours, 0=forever)
      [-pvPrefix=<PV name prefix>]
      [-noise=<rateSeconds>]
      [-arraySize=<bytes>] (sets EPICS_CA_MAX_ARRAY_BYTES)
      [-epicsBase=<path>]
      [-help] | [-h]
\end{verbatim}

\item \textbf{switches:}
\begin{itemize}
  \item {\tt -masterPVFile} --- SDDS file containing IOC PV names. Used to ensure no duplicate PVs are created.
  \item {\tt -pcasPVFile} --- SDDS file tracking PVs served by PCAS-style servers. Used to prevent duplicate PV advertisements.
  \item {\tt -standalone} --- Do not use the master PV files unless explicitly provided.
  \item {\tt -executionTime} --- How long to run in seconds. Values less than 0.5 are treated as ``forever''.
  \item {\tt -pvPrefix} --- Prefix prepended to all PV names.
  \item {\tt -noise} --- Periodically adds small random noise to numeric PV values.
  \item {\tt -arraySize} --- Sets \verb+EPICS_CA_MAX_ARRAY_BYTES+ for waveform transfers.
  \item {\tt -epicsBase} --- Path to an EPICS Base installation containing \verb+startup/EpicsHostArch+ and \verb+bin/<arch>/softIoc+.
  \item {\tt -debugLevel} --- Increase diagnostic output.
\end{itemize}

\item \textbf{see also:}
\begin{itemize}
  \item \progref{sddspcas}
  \item \progref{cavget}
  \item \progref{cavput}
\end{itemize}

\item \textbf{author:} Robert Soliday, ANL/APS.
\end{sddsprog}
