% Template for making SDDS Toolkit manual entries.
\begin{latexonly}
\newpage
\end{latexonly}

\subsection{sddswget}
\label{sddswget}

\begin{itemize}
\item {\bf description:}
\verb+sddswget+ reads waveform process variables and writes the values to a binary SDDS file.  Waveform PV names may come from an SDDS input file or from the command line.  Each output page contains a single waveform with time stamps.

\item {\bf example:}
The following command fetches two waveform PVs and stores them in an SDDS file:
\begin{verbatim}
sddswget -PVnames=rf:wave1,rf:wave2 waveforms.sdds
\end{verbatim}

\item {\bf synopsis:}
\begin{verbatim}
sddswget
    [<inputfile> [-inputStyle={wget|wmonitor|automatic}] | -PVnames=<name>[,<name>]]
    <outputfile> [-pendIOtime=<seconds>] [-pipe[=input][,output]]
    [-provider={ca|pva}]
Writes values of process variables to a binary SDDS file.
\end{verbatim}

\item {\bf files:}
The output file contains parameters \verb+Time+, \verb+TimeStamp+, and \verb+WaveformPV+ along with columns \verb+Index+ and the waveform data.

\item {\bf switches:}
    \begin{itemize}
        \item {\tt -PVnames=<name>[,<name>]} --- list waveform PVs on the command line.
        \item {\tt -inputStyle={wget|wmonitor|automatic}} --- choose how PV names are read from the input file.  Wmonitor style expects a \verb+WaveformPV+ column; wget style uses a \verb+WaveformPV+ parameter.
        \item {\tt -pendIOtime=<seconds>} --- EPICS connection timeout.
        \item {\tt -pipe[=input][,output]} --- standard SDDS Toolkit pipe option.
        \item {\tt -provider={ca|pva}} --- select EPICS Channel Access (default) or PVAccess.
    \end{itemize}

\item {\bf see also:}
    \begin{itemize}
        \item \progref{sddswmonitor}
        \item \progref{sddswput}
    \end{itemize}

\item {\bf author: M. Borland, ANL/APS}
\end{itemize}
