%
% Template for making SDDS Toolkit manual entries.
%
\begin{latexonly}
\newpage
\end{latexonly}

%
% Substitute the program name for sddsvexperiment
%
\subsection{sddsvexperiment}
\label{sddsvexperiment}

\begin{itemize}
\item {\bf description:}
%
% Insert text of description (typicall a paragraph) here.
%
\verb+sddsvexperiment+ varies process variables and measures process variables, with optional averaging.
An input file of namelist commands gives the specific instructions.
The results are recorded in one or more SDDS files. This command differs from
\verb+sddsexperiment+ in that the measurement process variables are specified in two lists.  The first
list gives PV ``rootnames''.  The second list gives suffixes to apply to each of 
the rootnames.
\item {\bf example:} 
%
% Insert text of examples in this section.  Examples should be simple and
% should be proceeded by a brief description.  Wrap the commands for each
% example in the following construct:
% 
%
The strength of a storage ring horizontal corrector (S1A:H1) is varied while the readbacks at all horizontal beam position
monitors are recorded. The output file is S1A:H1.sdds.
\begin{verbatim}
sddsvexperiment S1A:H1.vexp S1A:H1.sdds
\end{verbatim}

where the contents of the file \verb+S1A:H1.exp+ are
\begin{verbatim}
&rootname_list 
        filename=bpmRoot.sdds
&end
&suffix_list 
        filename=bpmSuffix.sdds
&end

&variable PV_name = "S1A:H1:CurrentAO",
        parameter_name="S1A:H1"
! the corrector is varied in 5 steps from -1.0 to 1.0 amps.
        index_number = 0, index_limit = 5,
        initial_value = -1.0, final_value = 1.0,
&end
        
&execute
        post_change_pause=4,
        intermeasurement_pause=1
&end
\end{verbatim}
where the line starting with a ``!'' is a comment.

The contents of the file \verb+bpmRoot.sdds+ is
\begin{verbatim}
SDDS1
&description &end
&column
 name = "Rootname",  type = "string", &end
&data
 mode = "ascii", &end
360     ! number of rows
S1A:P1
S1A:P2
S1A:P3
S1A:P4
S1B:P5
S1B:P4
S1B:P3
S1B:P2
S1B:P1
S2A:P1  
...
\end{verbatim}
The contents of the file \verb+bpmSuffix.sdds+ is
\begin{verbatim}
SDDS1
&description &end
&column name=Suffix, type=string &end
&column name=NumberToAverage, type=long &end
&data mode=ascii, no_row_counts=1 &end
:ms:x   10
:ms:y   10
\end{verbatim}

\item {\bf synopsis:} 
%
% Insert usage message here:
%
\begin{verbatim}
usage: sddsvexperiment  <inputFile> <outputFile>
[-suffixFile=<filename>] [-rootnameFile=<filename>]
[-echoinput] [-dryrun] [-summarize] [-verbose[=very]] 
[-ezcaTiming=<timeout>,<retries>] [-describeInput]
\end{verbatim}
\item {\bf files:}
\begin{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% input file
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {\bf input file:}\par
The input file consists of namelist commands that set up and execute the experiment. The functions of the commands
are described below.
\begin{itemize}
   \item {\verb+variable+} --- specifies a process variable to vary,
      and the range and steps of the variation. More than one variable
      command may be defined, so that many process variables may vary
      at a time.

   \item {\verb+rootname_list+} --- specifies rootnames from which to
      generate process variable to measure at each step during the
      experiment.

   \item {\verb+suffix_list+} --- specifies suffixes from which to
      generate process variable to measure at each step during the
      experiment.

   \item {\verb+execute+} --- start executing the experiment. One
      group of variable, measurement and execute commands may follow
      another in the same file for multiple experiments.

   \item {\verb+erase+} --- deletes previous variable or measurement
      setups.

   \item {\verb+list_control_quantities+} --- makes a cross-reference
      file for process variable names and column names of the data
      file.

   \item {\verb+system_call+} --- specifies a system call (usually a
       script) to be executed either before a measurement or before
       setting a process variable.
\end{itemize}
The following text describes all the namelist commands and their
respective fields in more detail.  The command definition listing is
of the form

\begin{verbatim}
&<command-name>
    <variable-type> <variable-name> = <default-value>
    .
    .
    .
&end
\end{verbatim}

where the part \verb+<variable-type>+, which doesn't appear in an
actual command, is used to illustrate the valid type of the value. The
three valid types are:
\begin{itemize}
   \item \verb+double+ --- for a double-precision type, used for most
   physical quantity variables,
   \item \verb+long+ ---   for an integer type, used for flags mostly.
   \item \verb+STRING+ --- for a character string enclosed in double quotes.
\end{itemize}
An actual namelist in an input file should look like this:
\begin{verbatim}
&<command-name>
    [<variable-name> = <value>,]
    ...
&end
\end{verbatim}

In the namelist definition listings the square brackets denotes an
optional component.  Not all variables need to be defined -- the
defaults may be sufficient.  Those that do need to be defined are
noted in the detailed explanations.  The only variables that don't
have default values in general are string variables.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% this extra level of itemization is required to make the html output look
% good.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{htmlonly}
%\begin{itemize}
%\end{htmlonly}

\begin{latexonly}
\newpage\begin{center}{\Large \verb+variable+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+variable+}
\end{htmlonly}

\begin{itemize}
   \item function: Specifies a process variable to vary, and the range
      and steps of the variation.  Values of variables at each
      measurement step are written to an SDDS output file.  The
      readback-related fields are used to confirm that the physical
      device has responded to a setpoint command at every step (and
      substep) within some tolerance. Readback is enabled when
      {\verb+readback_attempts+} and {\verb+readback_tolerance+} are
      defined with non-zero positive values.

      When an arbitrary sequence of setpoint values is required (say a
      binary sequence), the values can be read in from an SDDS file
      specified by the {\verb+values_file+} field.  The fields
      associated for the range and steps are ignored in this case.

      With multiple \verb+variable+ commands, variables may be varied
      in a multi-dimensional grid.  For example, variables may be
      varied independently of each other, or some groups of variables
      may vary together forming one axis of a multi-dimensional grid
      (see item {\verb+index_number+}).

\begin{verbatim}
&variable
        STRING PV_name = NULL
        STRING parameter_name = NULL
        STRING symbol = NULL
        STRING units = "unknown"
        double initial_value = 0
        double final_value = 0
        long relative_to_original = 0
        long index_limit = 0
        long index_number = 0
        STRING function = NULL
        STRING values_file = NULL;
        STRING values_file_column = NULL;
        long substeps = 1
        double substep_pause = 0
        double range_multiplier = 1
        STRING readback_name = NULL
        double readback_pause = 0.1
        double readback_tolerance = 0
        long readback_attempts = 10
        long reset_to_original = 1
&end        
\end{verbatim}
   \item {\verb+PV_name+} --- Required. Process variable name to vary.

   \item {\verb+parameter_name+} --- Required. Parameter name for the
   variable data recorded in the output file.

   \item {\verb+symbol+} --- Optional. Symbol field for the above
   column definition of the variable data.

   \item {\verb+units+} --- Optional. Units field for the above column
   definition of the variable data.

   \item {\verb+initial_value+} --- Required. The initial value of the
   process variable in the variation.

   \item {\verb+final_value+} --- Required. The final value of the
   process variable in the variation.

   \item {\verb+index_limit+} --- Number of steps in the
   variation. Measurements are taken at each step.

   \item {\verb+index_number+} --- Required. The counter (or index)
      number with which the defined variation is associated. In a
      \verb+sddsexperiment+ run, counters must be defined in an
      increasing sequence starting from counter 0. That is, the first
      {\verb+variable+} command of the file must have
      {\verb+index_number+} = 0. The second {\verb+variable+} command
      must have {\verb+index_number+} = 0 or 1. In the former case,
      the two variables will move together with the same number of
      steps according their respective {\verb+initial_value+} and
      {\verb+final_value+}. In the latter case, the two variables will
      vary independently of each other with possibly different number
      of steps in a 2-dimensional grid.

      Counter number $n$ is nested within counter $n+1$. Therefore it
      might be efficient to assign devices with slower response times
      to higher \verb+index_number+ counter.

   \item {\verb+index_limit+} --- Normally required.  Number of steps
      in the variation. Measurements are taken at each step.  When
      more than one variable is associated with the same counter, only
      the {\verb+index_limit+} of the first variable definition for
      that counter need to be defined.  If {\verb+index_limit+} is
      defined in {\verb+variable+} commands of the same
      {\verb+index_number+} value, then the first {\verb+index_limit+}
      remain in force.

   \item {\verb+relative_to_original+} --- Optional. If non-zero, then
      the variation range is defined relative to the original process
      variable value (i.e. the value prior to running the program).

   \item {\verb+range_multiplier+} --- Optional. Factor by which the
      range, {\verb+final_value+} - {\verb+initial_value+}, is
      multiplied.  New values of {\verb+initial_value+} and
      {\verb+final_value+} are calculated while keeping the midpoint
      of the range the same.

   \item {\verb+function+} --- Optional. A string of rpn operations
      used to transform the range specified by {\verb+initial_value+},
      {\verb+final_value+}, and {\verb+index_limit+}. For convenience,
      the original value of the process variable, and the calculated
      grid value for the process variable on the current step or
      substep are automatically pushed onto the the stack before the
      function is executed. The calculated values are recorded in the
      output file. The environment variable \verb+RPN_DEFNS+ is used
      to read a rpn definition file at the start of the execution of
      \verb+sddsvexperiment+.

   \item {\verb+values_file+} --- Optional. An SDDS data file
      containing setpoints for the variable.  This is useful is one
      has arbitrary setpoints values to apply.  The values of the
      fields {\verb+initial_value+}, {\verb+final_value+},
      {\verb+_substeps+}, {\verb+range_multiplier+} and
      {\verb+index_limit+} are ignored.

      One can have other \verb+variable+ namelists with the same
      \verb+index_number+ that don't use a file for the values.  The
      default {\verb+index_limit+} of the other variable will be set
      to the number of setpoint in the values file.  Thus the values
      in the file and the values calculated for the other variable
      will vary together with the same number of steps.

   \item {\verb+values_file_column+} --- Required when
      {\verb+values_file+} is specified.  {\verb+values_file_column+}
      gives the column name of the setpoints data in file
      {\verb+values_file+}.

   \item {\verb+substeps+} --- Optional. If greater than one, the
      steps are subdivided into this number.  Measurements are not
      made at substeps. Substeps are useful when the physical device
      associated with the process variable cannot reliably make steps
      as large as those that might be defined with
      {\verb+initial_value+}, {\verb+final_value+}, and
      {\verb+index_limit+}.

   \item {\verb+substep_pause+} --- Optional. Number of seconds to
      pause after the variable change of each substeps.

   \item {\verb+readback_name+} --- Optional. Readback process
      variable name associated with {\verb+PV_name+}. The default
      value for {\verb+readback_name+} is {\verb+PV_name+}.

   \item {\verb+readback_tolerance+} --- Optional. Maximum acceptable
      absolute value of the difference between the process variable
      setpoint and its readback. A positive value is required in order
      to enable readbacks.

   \item {\verb+readback_pause+} --- Optional. Number of seconds to
      pause after each reading of the {\verb+readback_name+} process
      variable.  This pause time is in addition to other pauses
      defined.

   \item {\verb+readback_attempts+} --- Optional. Number of allowed
       readings of the {\verb+readback_name+} process variable and
       readback pauses after a variable change has occured.  After
       this number of readings, the program exits.  The first readback
       is attempted immediately (i.e. no pause) after sending a
       setpoint command to the {\verb+PV_name+}.  A positive value is
       required in order to enable readbacks.

   \item {\verb+reset_to_original+} --- Optional. A value of 1 means
       that the variable is reset to its original value when the
       experiment terminates normally or abnormally.
\end{itemize}


\begin{latexonly}
\newpage\begin{center}{\Large \verb+rootname_list+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+rootname_list+}
\end{htmlonly}

\begin{itemize}
   \item function: specifies rootnames from which to generate names of process variable to measure at each step during the experiment.
\begin{verbatim}
&rootname_list
        STRING filename = NULL;
&end
\end{verbatim}
   \item {\verb+filename+} --- Required. See description of rootname file below.
\end{itemize}

\begin{latexonly}
%\newpage
\begin{center}{\Large \verb+suffix_list+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+suffix_list+}
\end{htmlonly}
\begin{itemize}
   \item function: specifies suffixes from which to generate names of process variable to measure at each step during the experiment.
\begin{verbatim}
&suffix_list
        STRING filename = NULL;
&end
\end{verbatim}
   \item {\verb+filename+} --- Required. See description of suffix file below.
\end{itemize}

\begin{latexonly}
\newpage\begin{center}{\Large \verb+execute+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+execute+}
\end{htmlonly}
\begin{itemize}
   \item function: start executing the experiment. Some global parameters are defined here.
\begin{verbatim}
&execute
        double post_change_pause = 0
        double intermeasurement_pause = 0
        double rollover_pause = 0
        long post_change_key_wait = 0
        long allowed_timeout_errors = 1
        long allowed_limit_errors = 1
        double outlimit_pause = 0.1
        long repeat_reading = 1
        double post_reading_pause = 0.1
        double ramp_pause = 0.25;
        long ramp_steps = 10;
&end
\end{verbatim}
   \item {\verb+post_change_pause+} ---  Optional. Number of seconds to pause after each change before
      attempting to make any measurement.

   \item {\verb+intermeasurement_pause+} --- Optional. Number of
      seconds to pause between each measurement.  Individual
      measurements for averaging are taken at this interval.

   \item {\verb+rollover_pause+} --- Optional. Number of seconds to
      pause after a counter has reached its upper limit, and must
      rollover to zero. This allows any physical devices associated
      with the counter to settle after a change equal to the total
      range of the variation.

   \item {\verb+post_change_key_wait+} --- Optional. If non-zero, then
      wait for a key press after making variable changes but before
      taking measurements. A prompt is given.

   \item {\verb+allowed_timeout_errors+} --- Optional. Number of
      timeout errors allowed before aborting the program.

   \item {\verb+allowed_limit_errors+} --- Optional. Number of invalid
      range measurement errors allowed before aborting the
      program. The valid range of a measurement is specified in the
      {\verb+measurement+} command.

   \item {\verb+outlimit_pause+} --- Optional. Number of seconds to
      pause after an invalid range measurement error occured. This is
      to permit equipment time to recover from whatever glitch caused
      the out-of-limit reading.

   \item {\verb+repeat_reading+} --- Optional. The measurements and
      statistical analyses are repeated this number of times for each
      variable settings. A page of data is written to the output file
      for each repitition.

   \item {\verb+post_reading_pause+} --- Optional. Number of seconds
      to pause after taking a set of measurements and making a
      statistical analysis.  If measurements are repeated then the
      pause is repeated after each set of measurements.

   \item {\verb+ramp_steps+} --- Optional. Number of steps in the
      variables PV ramp which occurs at the start and the end of the
      experiment.

      Ramping is necessary for some devices that do not respond well
      to large changes to their setpoints. Ramping is done at the
      start of the experiments to slowly change the variable PVs from
      their current values to their initial values. Another ramp is
      done at the end to slowly bring the variable PVs from their
      final values back the original values. Ramping back to original
      values is also done when the experiment aborts for some reason.

   \item {\verb+ramp_pause+} --- Optional. Time interval at each step
      of the variables PV ramp which occurs at the start and the end
      of the experiment. This is not the same variable as the pause
      between variable changes during the experiment.
\end{itemize}

\begin{latexonly}
\newpage\begin{center}{\Large \verb+erase+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+erase+}
\end{htmlonly}
\begin{itemize}
   \item function: deletes previous variable or measurement setups.
\begin{verbatim}
&erase
        long variable_definitions = 1
        long measurement_definitions = 1
&end
\end{verbatim}
   \item {\verb+variable_definitions+} --- Optional. If non-null, then all the variable definitions are erased.
   \item {\verb+measurement_definitions+} --- Optional. If non-null, then all the measurement definitions are erased.
\end{itemize}

\begin{latexonly}
%\newpage
\begin{center}{\Large \verb+list_control_quantities+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+list_control_quantities+}
\end{htmlonly}
\begin{itemize}
   \item function: makes a cross-reference file for process variable names and column names of the data file.
\begin{verbatim}
&list_control_quantities
         STRING filename = NULL
&end
\end{verbatim}
   \item {\verb+filename+} --- Required. Name of file. Columns defined are \verb+ControlName+,
                \verb+SymbolicName+, and \verb+ControlUnits+.
\end{itemize}

\begin{latexonly}
\newpage\begin{center}{\Large \verb+system_call+}\end{center}
\end{latexonly}
\begin{htmlonly}
\item {\Large \verb+system_call+}
\end{htmlonly}
\begin{itemize}
   \item function: specifies a system call (usually a script) to be executed repeatedly during the experiment.
\begin{verbatim}
&system_call
        STRING command = NULL
        long index_number = 0
        long index_limit = 0
        double post_command_pause = 0
        double pre_command_pause = 0
        long append_counter = 0
        STRING counter_format = "%ld"
        long call_before_setting = 0
        long call_before_measuring = 1
        STRING counter_column_name = NULL 
&end       
\end{verbatim}
   \item {\verb+command+} --- Required. Name of shell command or script to execute.
   \item {\verb+index_number+} --- Required. Counter number with which the command will be associated. The command is executed
                when this counter is advanced or rolled over.
   \item {\verb+index_number+} --- Optional. Number of times the command is executed for 
                the associated counter. This field is used only when the value of {\verb+index_number+} above defines a new counter.
   \item {\verb+post_command_pause+} --- Optional. Number of seconds to pause after the completion of the command.
   \item {\verb+pre_command_pause+} --- Optional. Number of seconds to pause before executing the command.
   \item {\verb+append_counter+} --- Optional. If non-zero, the counter value is appended to the command when the
                system call is made.
   \item {\verb+counter_format+} --- Optional. Format for the counter if the counter value is appended to the command.
   \item {\verb+call_before_setting+}, {\verb+call_before_measuring+}, --- Optional.
                At a counter advance or rollover
                the command can be executed in one of three ways:
                \begin{itemize}
                   \item  before both variable changes and measurements: \\
                        {\verb+call_before_setting+}=1, {\verb+call_before_measuring+}=1
                   \item  after variable changes and before measurements:\\
                        {\verb+call_before_setting+}=0, {\verb+call_before_measuring+}=1
                   \item  after both variable changes and measurements:\\
                        {\verb+call_before_setting+}=0, {\verb+call_before_measuring+}=0
                \end{itemize}
                If multiple measurements are made for averaging, the command is not executed between measurements.
   \item {\verb+counter_column_name+} --- Optional. If non-null, a column in the output file with this name is defined.
                The values written to this column are the number of times the command had been called minus one. This
                value doesn't rollover with its associated counter.
\end{itemize}

%\begin{htmlonly}
%\end{itemize}
%\end{htmlonly}

\newpage
\item {\bf Rootname file:} \par
        SDDS file defining the rootnames of the process variables with colum:
                \begin{itemize}
           \item  {\verb+Rootname+} --- Required string column to generate measurement process variables.
                \end{itemize}

\item {\bf Suffix file:} \par
        SDDS file defining the suffixes and measurement parameters with columns:
                \begin{itemize}
           \item {\verb+Suffix+} --- Required string columne of suffix names to be appended to the \verb+Rootname+
                         values in the rootname file to generate measurement process variables.
           \item {\verb+ColumnNameSuffix+} --- Optional string column of names of suffix column appearing in output data file.
           \item {\verb+NumberToAverage+} --- Optional long column of number of measurements to average.
           \item {\verb+IncludeStDev+} --- Optional character column. If value is 
                        ``y'' then the standard deviation (a measure of the distribution of 
                        measurements) is calcualted and included
                        in the output file. If ``n'' then the standard deviation is not calculated.
           \item {\verb+IncludeSigma+} --- Optional character column. If value is ``y'' then the sigma (uncertainty on the mean value) 
                        is calcualted and included
                        in the output file. If ``n'' then the sigma is not calculated.
           \item {\verb+LowerLimit+} and {\verb+UpperLimit+} --- Optional double columns.
                         Must have both or neither. Defines a range of validity for the
                        individual measurements. If the number of invalid measurements (reset to 0 at each
                        measurement step) equals or exceeds the value
                        of {\verb+allowed_limit_errors+} (default of 1) in command {\verb+execute+}, then the program aborts.
                        The average values written to the output file excludes measurements outside this range.
                \end{itemize}

\item {\bf Output file:}\par
The output file contains one data page for each variable step.
The names of the defined columns are those string data of the {\verb+Suffix+} or {\verb+ColumnNameSuffix+} 
columns from the suffix file.
A column is created for each standard deviation or sigma calculation requested for a measurement.
The standard deviation columns are named \verb+StDev<columnName>+, and
the sigma columns are named \verb+StDev<columnName>+, where \verb+<columnName>+ is replaced
by an actual column name.

Some additional columns are defined:
\begin{itemize}
   \item {\verb+Rootname+} --- String column for the rootname of the PVs.
   \item {\verb+Index+} --- Long columns for the index of the row.
   \item {\tt Time} --- Double parameter of time since start of epoch. This time data can be used by
        the plotting program {\verb+sddsplot+} to make the best coice of time unit conversions
        for time axis labeling.
   \item {\tt ElapsedTime} --- Double parameter of elapsed time of readback since the start of the experiment.
\end{itemize}

The variable values appear as parameters in each data page.

Many time parameters are defined:
\begin{itemize}
   \item {\verb+Step+} --- Long parameter for the step number.
   \item {\tt Time} --- Double parameter of time since start of epoch. This time data can be used by
        the plotting program {\verb+sddsplot+} to make the best coice of time unit conversions
        for time axis labeling.
   \item {\tt ElapsedTime} --- Double parameter of elapsed time of readback since the start of the experiment.
   \item {\tt TimeOfDay} --- Double parameter of system time in units of hours. 
                The time does not wrap around at 24 hours.
   \item {\tt TimeStamp} --- String parameter of time stamp for file.
\end{itemize}

\end{itemize}

\item {\bf switches:}
%
% Describe the switches that are available
%
   \begin{itemize}
   \item {\verb+-suffixFile=<filename>+} --- SDDS file defining the suffixes and measurement parameters. If not specified
                on the command line, then the namelist command {\verb+suffix_list+} is required in the input file.
   \item {\verb+-rootnameFile=<filename>+} --- SDDS file defining the rootnames of the process variables. If not specified
                on the command line, then the namelist command {\verb+rootname_list+} is required in the input file.
    \item {\verb+-echoinput+} --- echos input file to stdout.
    \item {\verb+-dryrun+} --- the ``variable'' process variables are left untouched during the execution. The ``measurement''
                process variables are still read. The pauses and system calls are still in effect.
    \item {\verb+-summarize+} --- gives a summary of the experiment before executing it.
    \item {\verb+-verbose[=very]+} --- prints out information during the execution such as notification of 
                setting and reading process variables.  The option \verb+very+ prints out the average measurement values.
    \item {\verb+-ezcaTiming=<timeout>,<retries>+} --- sets EZCA timeout and retry parameters
    \item {\verb+-describeinput+} --- Printouts the list of namelist commands and fields of the input file.
    \end{itemize}

\item {\bf see also:}
    \begin{itemize}
%
% Insert references to other programs by duplicating this line and 
% replacing <prog> with the program to be referenced:
%
    \item \progref{sddsexperiment}
    \end{itemize}
%
% Insert your name and affiliation after the '}'
%
\item {\bf author: M. Borland, ANL} 
\end{itemize}
