%
% Documentation for sddscainfo
%
\begin{sddsprog}{sddscainfo}
\item \textbf{description:}
  \verb+sddscainfo+ reads a list of process variable (PV) names from an SDDS file,
  queries the control system for metadata, and writes the results to an SDDS output file.
  The program can also create input files for \progref{sddspvalogger} or \progref{sddspvasaverestore}.

\item \textbf{examples:}
  Gather connection information for the PVs listed in \verb+pvList.sdds+ and write the results to \verb+pvInfo.sdds+.
  \begin{verbatim}
sddscainfo pvList.sdds pvInfo.sdds
  
\end{verbatim}
  Create a metadata file and a corresponding input for \progref{sddspvalogger}.
  \begin{verbatim}
sddscainfo pvList.sdds pvInfo.sdds -makeLoggerInput
  
\end{verbatim}
  Create a metadata file and a corresponding input for \progref{sddspvasaverestore}.
  \begin{verbatim}
sddscainfo pvList.sdds pvInfo.sdds -makeSCRInput
  
\end{verbatim}

\item \textbf{synopsis:}
  \begin{verbatim}
usage: sddscainfo [<inputfile>] [<outputfile>]
[-pipe=[input][,output]]
[-makeLoggerInput[=withStorageType]]
[-makeSCRInput]
[-verbose]
[-pendIOTime=<seconds>]
  
\end{verbatim}

\item \textbf{files:}
\begin{itemize}
  \item \textbf{input file:} SDDS file with string column \verb|ControlName| listing PVs to query.
  \item \textbf{output file:} SDDS file containing metadata for each PV.
\end{itemize}

\item \textbf{switches:}
\begin{itemize}
  \item {\tt -pipe[=input][,output]} --- read from standard input and/or write to standard output.
  \item {\tt -makeLoggerInput[=withStorageType]} --- write an input file for \progref{sddspvalogger}; append \newline
    \verb|withStorageType| to include the storage type.
  \item {\tt -makeSCRInput} --- write an input file for \progref{sddspvasaverestore}.
  \item {\tt -verbose} --- print PV metadata to the terminal.
  \item {\tt -pendIOTime=<seconds>} --- time to wait for Channel Access operations (default 0.5 s).
\end{itemize}

\item \textbf{see also:}
\begin{itemize}
  \item \progref{sddspvalogger}
  \item \progref{sddspvasaverestore}
\end{itemize}

\item \textbf{author:} Robert Soliday, ANL/APS.
\end{sddsprog}
