%
% Template for making SDDS Toolkit manual entries.
%
\begin{latexonly}
\newpage
\end{latexonly}

%
% Substitute the program name for toggle
%
\subsection{toggle}
\label{toggle}

\begin{itemize}
\item {\bf description:}
%
% Insert text of description (typically a paragraph) here.
%
\verb+toggle+ alternates between two sets of process variable values stored in 
snapshot files and/or
process variables specified on the command line.
Time intervals and the values of the process variables upon termination can be specified.
\item {\bf example:} 
%
% Insert text of examples in this section.  Examples should be simple and
% should be proceeded by a brief description.  Wrap the commands for each
% example in the following construct:
% 
%
Two states of the APS storage ring injection magnets are restored for 10 seconds each by writing 
values of process variables listed in the snapshot files SRin.snp1 and SRin.snp2:
\begin{verbatim}
toggle SRin.snp1 SRin.snp2 interval=10,10
\end{verbatim}
In this case the magnets return returns to the initial state upon termination.

\item {\bf synopsis:} 
%
% Insert usage message here:
%
\begin{verbatim}
usage: toggle [snapshotfile1 [snapshotfile2]] [-controlname=PVname,value1[,value2] ...]
       [-interval=interval1[,interval2]] [-cycles=number] [-finalset={0|1|2}]
       [-prompt] [-verbose] [-warning]
\end{verbatim}

\item {\bf files:}
% Describe the files that are used and produced
\begin{itemize}
\item {\bf input files:}\par
The input files are valid snapshot files as described in \progref{burtwb}. At least three
columns must be defined:
\begin{itemize}
        \item {\tt ControlName} --- Required column. String column for the process variable or device name.
        \item {\tt ControlType} --- Required column. String column for the control name type. For a 
                process variable name use ``pv''; for a device name use ``dev''.
        \item {\tt ValueString} --- String column containing the value to be restored as a character string.
\end{itemize}
Optional columns are:
\begin{itemize}
        \item {\tt RestoreMsg} --- Optional column. String column for the device set message if 
                the {\tt ControlType} value is ``dev''.
                If this column is absent then the default read message is ``set''.
\end{itemize}
        Both files must have the same set of PV names.
\end{itemize}
%
\item {\bf switches:}
%
% Describe the switches that are available
%
    \begin{itemize}
%
%   \item {\tt -pipe[=input][,output]} --- The standard SDDS Toolkit pipe option.
%
        \item {\tt -controlname=<PVname>,<value1>[,<value2>]} --- Optional. Specified a PV to be 
                alternated. If only one value is given, then the second value
                is taken to be pre-existing. These values are synchronized with
                the snapshot files if they are present.
        \item {\tt -interval=<interval1>[,<interval2>]} ---  Optional. \verb+<interval1>+ and \verb+<interval2>+
                 are the durations of PV value sets 1 and 2, respectively.
                 If \verb+<interval2>+ isn't present, then \verb+<interval2>+=\verb+<interval1>+.
                 If this option isn't present, then the default interval is 1 second each.
        \item {\tt -cycles=<number>} --- Optional number of cycles. Default is 1.
        \item {\tt -finalset=\{0|1|2\}} --- Optional. Specifies which PV value set to apply at normal termination.
                 0,1, and 2 mean set of pre-existing values, first set and second
                 set respectively. During abnormal termination, the PVs are
                 returned to their pre-existing values.
        \item {\tt -prompt} --- Optionally toggles values only on a \verb+<CR>+ key press.
        \item {\tt -verbose} --- Optionally prints extra information.
        \item {\tt -warning} --- Optionally prints warning messages.
    \end{itemize}

\item {\bf see also:}
    \begin{itemize}
%
% Insert references to other programs by duplicating this line and 
% replacing <prog> with the program to be referenced:
%
    \item \progref{burtwb}
    \end{itemize}
%
% Insert your name and affiliation after the '}'
%
\item {\bf author: L. Emery, ANL} 
\end{itemize}
